Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-27 be.tex
caption

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} Mininmum value for ratio of the stagnation
  radius to the influence radius, $\rs/\rsoi$ for core galaxies
  ($\Gamma=0.1$) derived by requiring enthalpy of the gas to remain
  positive out to the break radius $\rb$. The solid lines correspond
  to the constraint computed numerically from
  equation~\eqref{eq:enthAnal}, while the dashed line correspond the
  results of the fitting formula equation~\eqref{eq:rsRinfCrit}. The
  x-intercept of each curve corresponds to the critical $\zeta$,
  $\zeta_c$ above which an outflow is possible from any radius}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical
  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$. If $\zeta<\zeta_c$ outflows are
  only possible if the ratio of the stagnation radius to the influence
  radius exceeds a minimum value. Plotted as a function of the ratio
  of the break radius to the influence radius ($\rb/\rsoi$) {\emph Bottom
    Panel:} Mininmum value for ratio of the stagnation radius to the
  influence radius, $\rs/\rsoi$ for core galaxies ($\Gamma=0.1$)
  derived by requiring enthalpy of the gas to remain positive out to
  the break radius $\rb$. This is calculated numerically from
  equation~\eqref{eq:enthAnal}. The x-intercept of each curve
  corresponds to the critical $\zeta_c$}
\end{figure}
